Constant-sized correlations are sufficient for robust self-testing of maximally entangled states with unbounded dimension

### 2019-05-01 Draft/draft.tex
Honghao: edits of section 3

\begin{definition}
	Given sets $\calX, \calY, \calA, \calB$, a correlation is a collection of conditional probability distributions
	$\{\pr{ab}{xy}: a \in \calA, b \in \calB\}_{x \in \calX, y \in \calY}$.
\end{definition}
A particular type of nonlocal games that we are interested in is called linear system games, which is defined below.
\begin{definition}[Linear system game]
 Let $H\ux = \uc$ be an $m \times n$ system of linear equations over $\Z_2 = \{0, 1\}$,
 where $H$ is an $m$-by-$n$ matrix with entries in $\Z_2$ and 
 $\uc$ is a length-$n$ vector with entries in $\Z_2$. 
 The associated linear system game involves two
 players Alice and Bob, where Alice is given an equation number $i \in \calX = \{1 \dots m\}$ and replies with $\ua \in \calA = \Z_2^{\times n}$,
 and Bob is given a variable number $j \in \calY = \{1 \dots n\}$ and replies with an assignment $b \in \calB = \Z_2$. The 
 scoring function is defined by
 \begin{align}
 	V(\ua, b, i, j) =
	\begin{cases}
		1, \quad \text{if } \sum_{k= 1}^n H(i,k) \ua(k) \equiv c(i) \pmod 2 \text{ and } \ua(j) = b \\
		0,  \quad \text{otherwise.}
	\end{cases}
\end{align}
\end{definition}
In the rest of the paper, we will work with quantum strategies for the linear system game presented in terms of binary observables.
\begin{definition}[Quantum strategy of a linear system game]
\label{def:q_strat}
A quantum strategy presented in terms of binary observables for the linear system game $(H\ux = \uc)$ consists of 
\begin{enumerate}
	\item a pair of finite-dimensional Hilbert spaces $\calH_A$ and $\calH_B$; 
	\item a collection of binary observables $N_j$, $1 \leq j \leq n$, on $\calH_B$
	such that $N_j^2 = \1$ for every $1 \leq j \leq n$; 
	\item a collection of binary observables $M_{ij}$, $1\leq i \leq m$, $1\leq j\leq n$ 
	on $\calH_A$ such that 
	\begin{enumerate}
		\item $M_{ij}^2 = \1$ for every $i,j$,
		\item $\Pi_j M_{ij}^{H(i,j)} = (-\1)^{\uc(i)}$ for every $i$, and
		\item $M_{il}M_{ik} = M_{ik}M_{il}$ for every $i$ and $H(i,l) = H(i,k) =1$;
	\end{enumerate} 
	and
	\item a quantum state $\ket{\psi} \in \calH_A \x \calH_B$.
\end{enumerate}
\end{definition}
Note that any quantum strategy presented in terms of binary observables can be 
converted to a quantum strategy presented in terms of projective measurement by looking into
the spectral decompositions of the observables. 
\hf{More specifically, the fact that all the observables $\{M_{ij}\}_{j: H(i,j) = 1}$ commute with each other
implies that they share a common eigenspace. The collection of eigenvalues associated with one eigenstate is the assignment
to the whole equation when this eigenstate is measured in a projective measurement strategy.}
 \carl{If you're going to make that claim, you should make it more precise.  Add a sentence explaining briefly how the construction is done.}

@@

%=======================================
\section{The linear system game}
\label{sec:lsg}
%=======================================
In this section, we introduce a linear constraint test that is satisfied by our correlation.
The linear constraint test is designed to enforce relations that should be satisfied by 
Alice and Bob's observables and it is inspired by 
Slofstra's seminal work~\cite{slofstra2017}, in which he
embeds the group
\begin{align}
	K = \ip{ x,y,a,b:a^2=b^2=e, ab=ba, yay^{-1} = a, yby^{-1} = ab, xyx^{-1}=y^2}
\end{align}
into a linear system game such that the relations in the definition of $K$ can be derived from the
combination of the equations of the linear system game. Then he showed the difference between exact representations
and approximate representations of $K$, which implies that the set of quantum correlation is not closed.
\hf{We generalize the relation $xyx^{-1} = y^2$ and embed the 
following group}
\begin{align}
	G = \langle u, o : uou^{-1} = o^r \rangle, 
\end{align}
for some $r \in \N$ into a linear constraint test.

%------------------------------------------------------------------------
\subsection{The embedding of $G$}
%------------------------------------------------------------------------
The main result of this subsection is summarized in the following theorem.
\begin{theorem}
	The relation $uou^{-1} = o^r$ can be embedded in a linear constraint test which has
	$n(r) := 18r+86$ variables and $m(r) := 16r + 72$ equations, where each equation has $3$ variables.
\end{theorem}
We prove this by constructing the solution group $\Gamma$ of the linear constraint test. 
We also prove some properties of the generators of $\Gamma$ along the way.

We embed $G$ into $\Gamma$ in three steps and introduce two intermediate groups $G_0$ and $G_1$, which are defined below.
\begin{definition}
	The presentation of $G_0$ has order-$2$ generators:
	\begin{align}
		\{o_i\}_{i=1}^{r} \cup \{u_i\}_{i=1}^5
	\end{align}
	and relations:
	\begin{align}
	&u_3 = u_2o_1u_2 && u_4 = u_2o_2u_2 \\
	&u_5 = u_1u_3u_1 && o_2 = u_1u_4u_1\\
	&u_5 = o_1 o_r o_1,
	\end{align}
	and when $r$ is even
	\begin{align}
	&o_{1+2j} = o_1o_{2j}o_1 && o_{2+2j} = o_2o_{1+2j}o_2&& \text{ for } j = 1 \dots r/2 - 1;
	\end{align}
	when $r$ is odd
	\begin{align}
	&o_3 = o_2o_1o_2 &&
	 o_{2+2j} =o_1o_{1+2j}o_1 && o_{3+2j} = o_2o_{2j+2}o_2 &&\text{ for } j = 1 \dots (r-3)/2.
	\end{align}
\end{definition}
\begin{proposition}
	The group $G_1$ embeds the relation 
	\begin{align}
		(u_1u_2)^j o_1o_2 (u_2u_1)^j = (o_1o_2)^{r^j}, 
	\end{align}
	for any $ j \in \N$.
\end{proposition}
The proof follows the proof of Proposition~$4.8$ of Ref.~\cite{slofstra2017}
\begin{proof}
	We prove it by induction.
	Direct calculation gives us that
	\begin{align} 
		u_1u_2 o_1o_2 u_2u_1 = &u_1 (u_2 o_1u_2) (u_2o_2 u_2) u_1 \\
	=& (u_1 u_3 u_1) (u_1 u_4 u_1)\\
	=& u_5 o_2\\
	=& o_1o_ro_1 o_2.
	\end{align}
	Then substituting the definitions of $o_k$ for $k = r \dots 3$ gives us the case for $j=1$.

	Now assume the statement is true for $j = n$, then when $j = n+1$
	\begin{align}
		(u_1u_2)^{n+1} o_1o_2 (u_2u_1)^{n+1} =& u_1u_2 (o_1o_2)^{r^n} u_2u_1 \\ 
		 =& (u_1u_2 o_1o_2 u_2u_1)^{r^n} \\
		 =& (o_1o_2)^{r^{n+1}},
	\end{align}
	where from the first line to the second line, we insert $(u_2u_1)(u_1u_2)$ between every pair of $o_1o_2$ and $o_1o_2$.
	Hence, the statement is true.
\end{proof}
To better characterize all the conjugation relations above and simplify the form of $G_1$
and make the introduction of $G_2$ easier, we relabel $u_i$ and $o_i$'s
as $a_i$'s such that
\begin{align}
	a_j := 
	\begin{cases}
	 o_j \text{ for } j = 1,2 \\
	 u_{j-2} \text{ for } j = 3\dots 7 \\
	o_{j- 5} \text{ for } j = 8 \dots r+5.
	\end{cases}
\end{align}
Then we define the set $C(r)$ of tuples $(i,j,k)$ such that
\begin{align}
	(i,j,k) \in C(r) \iff a_ia_ja_i = a_k.
\end{align}
The size of $C(r)$ is $r+3$. 
%We can also employ some ordering of $C(r)$ such that $C(r,j)$ is a unique tuple for 
%$j = 1 \dots r+3$.
In this way, the group $G_0$ can be presented by
\begin{align}
	G_0  = \ip{ \{a_i\}_{i=1}^{r+5} : C(r) }.
\end{align}

Then we define the group $G_1$.
\begin{definition}
The presentation of $G_1$ has order-$2$ generators:
\begin{align*}
	\{a_i, b_i, c_i, d_i, v_i\}_{i=1}^{r+5}, f, g, \{h_{jk}\}_{(i,j,k) \in C(r)};
\end{align*}
and relations:
\begin{align*}
	&a_i = b_ic_i = fd_i = gv_i,&& fb_if =c_i &&\text{ for } i= 1 \dots r+5 \\
	&h_{jk}b_j c_k = e,&& d_ib_jd_i = c_k &&\text{ for all } (i,j,k) \in C(r).
\end{align*}
\end{definition}
Note that the group $G_1$ is slightly different from the group $K$ used in the proof of Lemma~$4.4$ of Ref.~\cite{slofstra2017}.
We introduce the generator $g$ so that later we can associate $f$ with $g$ in linear relations of the Magic Square game.
Such relations are important for the self-testing proof.
Two important properties of $G_1$ are given in propositions below.
The first property of $G_1$ was first proved in Lemma~$4.4$ of \cite{slofstra2017}.
\begin{proposition}
	The group $G_1$ embeds relation $x_ix_jx_i = x_k$ for all $(i,j,k) \in C(r)$.
\end{proposition}
\begin{proof}
	We first show that $d_i c_j d_i = b_k$, which is because
	\begin{align}
		d_i c_j d_i = d_i (f b_j f) d_i = f (d_i b_j d_i) f = f c_k f = b_k.
	\end{align}
	Then, we can prove that 
	\begin{align}
		a_i a_j a_i = f d_i b_j c_j f d_i = (f d_i b_j d_i f)(f d_i c_j d_i f) = (f c_k f)(f b_k f) = b_k c_k = a_k. 
	\end{align}
\end{proof}
\begin{proposition}
	In the group $G_1$, the generators $f$ and $g$ commute with $a_i$ for all $i = 1 \dots r+5$.
\end{proposition}
\begin{proof}
	We can check that
	\begin{align}
		fa_i f a_i = d_i d_i = e && g a_i g a_i = v_i v_i  = e,
	\end{align}
	for all $i = 1 \dots r+5$.
\end{proof}
Note that there are two types of conjugacy relations in $G_1$. One is of the form
$f b_i f = c_i$ for all $i = 1 \dots r+5$. The other one is of the form 
$d_ib_jd_i = c_k$ for all $(i,j,k) \in C(r)$. For each type of the conjugacy relations, 
we are going to embed it into a different set of linear relations in $\Gamma$.

\begin{definition}
\label{def:gamma}
The presentation of $\Gamma$ has order-$2$ generators:
\begin{align*}
	J, \{a_i, b_i, c_i, d_i, v_i,w_i,\{ k_{i,j} \}_{j=1}^5\}_{i=1}^{r+5}, \{f_i,g_i,m_i\}_{i=0}^2, \{h_{jk}\}_{(i,j,k) \in C(r)}, 
	\{\{ k_{c,j} \}_{j=1}^6\}_{c \in C(r)},
\end{align*}
and relations:
\begin{itemize}
\item for all $i = 1 \dots r+5$:
\begin{align}
	&a_i = b_ic_i = f_0d_i = g_0v_i \\
	&g_2 a_i w_i = e \\
	&f_0 f_1 f_2 = e && b_i f_2 k_{i,1} = e && k_{i,1} k_{i,2} k_{i,3} = e\\
	&f_0 k_{i,3} k_{i,4} = e && c_i k_{i,4} k_{i,5} =e && f_1 k_{i,2} k_{i,5} = e,
\end{align}
which embed $f_0 b_i f_0 = c_i$;
\item for all $ c = (i,j,k) \in C(r)$:
\begin{align}
	&h_{jk}b_j c_k = e\\
	&d_i k_{c,1} f_2 = e && b_j f_2 k_{c,2} = e && k_{c,2} k_{c,3} k_{c,4} = e\\
	&d_i k_{c,4} k_{c,5} = e && c_k k_{c,5} k_{c,6} =e && k_{c,1} k_{c,3} k_{c,6} = e,
\end{align}
which embed $d_i b_j d_i = c_k$;
\item relations of a Magic Square test:
\begin{align}
	&f_0 f_1 f_2 = e && g_0 g_1 g_2 = e &&m_0 m_1 m_2 = e \\
	&f_0 g_2 m_0 = e && f_2 g_0 m_1 = e && f_1 g_1 m_2 = J,
\end{align}
which embed $f_0 g_0 f_0 g_0 = J$ and $f_2 g_2 f_2 g_2 = J$;
\item $J$ commutes with all the other generators.
\end{itemize}
\end{definition}
The special properties of the generators of $\Gamma$ are summarized in the two propositions below.
\begin{proposition}
	The group $\Gamma$ embeds all the conjugacy relations of $G_1$.
	It also embeds the relations: $f_0 g_0 f_0 g_0 = J$ and $f_2 g_2 f_2 g_2 = J$.
\end{proposition}
The proof of the proposition above follows the proof of Proposition $4.2$ of Ref.~\cite{slofstra2017}.
\begin{proposition}
	In the group $\Gamma$, the generator $f_2$ commutes with $f_0$ and $a_i$ for all $i = 1 \dots r+5$;
	the generator $g_2$ commutes with $g_0$ and $a_i$ for all $i = 1 \dots r+5$.
\end{proposition}
\begin{proof}
	We show the commutativity property of $f_2$ as an example. The proof for $g_2$ is very similar.
	The commutativity between $f_0$ and $f_2$ is immediate from the relations.
	From the relation, we can also deduce that $f_2$ commutes with $b_i$ for all $i$.
	Since $a_i =b_ic_i = b_i f_0 b_i f_0$, we know $f_2$ commutes with $a_i$.
\end{proof}

%------------------------------------------------------------------------
\subsection{The representation of $\Gamma$}
%------------------------------------------------------------------------
In this section we give the presentation of $\Gamma$ which is built upon the representation 
$\Psi_0$ of $G_0$ and $\Psi_1$ of $G_1$. We need the representation of $\Gamma$ to construct the
ideal strategy that realizes our correlation.

Before giving the representation, we define two Hilbert spaces $W_{d-1}$ and $W_2$, which will form the carrier spaces
of the representations,
\begin{align}
	\label{eq:w_subspace}
	W_{d-1} := \spn(\{\ket{x_j}\}_{j=1}^{d-1}) && W_2 = \spn(\ket{x_1}, \ket{x_2}).
\end{align}
Note that another form of the basis of $W_{d-1}$ is $\{\ket{x_{r^j}}\}_{j=0}^{d-2}$, where the subscript $r^j$ is taken
modulo $d$ implicitly. We use the second form of the basis when it is convenient.
We denote the identity operator for these two spaces by $\1_{W_{d-1}}$ and $\1_{W_2}$.
On the Hilbert space $W_2$, we define
\begin{align}
	X_{W_2} = \ketbra{x_1}{x_2} + \ketbra{x_2}{x_1} &&
	Y_{W_2} = i\ketbra{x_1}{x_2} - i \ketbra{x_2}{x_1} &&
	Z_{W_2} = \ketbra{x_1}{x_1} - \ketbra{x_2}{x_2},
\end{align}
\begin{definition}
The representation, $\Psi_0$, of $G_0$ on $W_{d-1}$ is defined by
\begin{align}
	\Psi_0(a_1) =&\sum_{j=1}^{(d-1)/2} \omega_d^j \ketbra{x_j}{x_{d-j}} + \omega_d^{-j} \ketbra{x_{d-j}}{x_{j}} \\
	\Psi_0(a_2) = &\sum_{j=1}^{d-1} \ketbra{x_j}{x_{d-j}}\\
	\Psi_0(a_3) = &\ketbra{u_0}{u_0} +\omega_{d-1}^{(d-1)/2}\ketbra{u_{(d-1)/2}}{u_{(d-1)/2}}\\ + 
	&\sum_{k=1}^{(d-3)/2}\left( \omega_{d-1}^k\ketbra{u_k}{u_{d-1-k}} + \omega_{d-1}^{-k}\ketbra{x_{d-1-k}}{x_k}\right)\\ 
	\Psi_0(a_4) = &\ketbra{u_0}{u_0} +\ketbra{u_{(d-1)/2}}{u_{(d-1)/2}} \\+
	 &\sum_{k=1}^{(d-3)/2}\left(\ketbra{u_{d-1-k}}{u_k} + \ketbra{u_k}{u_{d-1-k}}\right),
\end{align}
where $\{ \ket{u_j} \}_{j=0}^{d-2}$ is a another basis of $W_{d-1}$ given by
\begin{align}
	\ket{u_k} = \frac{1}{\sqrt{d-1}} \sum_{j=0}^{d-2} \omega_{d-1}^{jk} \ket{x_{r^j}}.
\end{align}
The representation of the rest of the generators
can be constructed from $\Psi_0(a_1)$, $\Psi_0(a_2)$, $\Psi_0(a_3)$ and $\Psi_0(a_4)$ following the 
conjugation relations.
\end{definition}
We can check that
\begin{align}
	\Psi_0(a_1a_2) =  \sum_{j=0}^{d-2} \omega_d^{r^j} \ketbra{x_{r^j}}{x_{r^j}} &&
	\Psi_0(a_3a_4) =  \sum_{j=0}^{d-2} \ketbra{x_{r^{j-1}}}{x_{r^j}},
\end{align}
which satisfy the relation $\Psi_0(a_3a_4) \Psi_0(a_1a_2) \Psi_0(a_4a_3) = \Psi_0(a_1a_2)^r$ and
$[\Psi_0(a_3a_4), \Psi_0(a_2)] = \1_{W_{d-1}}$.

>>>>

\begin{definition}
	Given sets $\calX, \calY, \calA, \calB$, a correlation is a collection of conditional probability distributions
	$\{\pr{ab}{xy}: a \in \calA, b \in \calB\}_{x \in \calX, y \in \calY}$.
\end{definition}
A particular type of nonlocal games that we are interested in is called linear system games, which is defined below.
\begin{definition}[Linear system game]
 Let $H\ux = \uc$ be an $m \times n$ system of linear equations over $\Z_2 = \{0, 1\}$,
 where $H$ is an $m$-by-$n$ matrix with entries in $\Z_2$ and 
 $\uc$ is a length-$n$ vector with entries in $\Z_2$. 
 The associated linear system game involves two
 players Alice and Bob, where Alice is given an equation number $i \in \calX = \{1 \dots m\}$ and replies with $\ua \in \calA = \Z_2^{\times n}$,
 and Bob is given a variable number $j \in \calY = \{1 \dots n\}$ and replies with an assignment $b \in \calB = \Z_2$. The 
 scoring function is defined by
 \begin{align}
 	V(\ua, b, i, j) =
	\begin{cases}
		1, \quad \text{if } \sum_{k= 1}^n H(i,k) \ua(k) \equiv c(i) \pmod 2 \text{ and } \ua(j) = b \\
		0,  \quad \text{otherwise.}
	\end{cases}
\end{align}
\end{definition}
\hf{A widely-used example of linear system games is the Magic Square game introduced in Ref.~\cite{magic_square}.
For the formulation of the Magic Square game as a linear system game
and the general linear system games over $\Z_d$, we refer to Section $3.1$ of Ref.~\cite{coladan2017}.}

In the rest of the paper, we will work with quantum strategies for the linear system game presented in terms of binary observables.
\begin{definition}[Quantum strategy of a linear system game]
\label{def:q_strat}
A quantum strategy presented in terms of binary observables for the linear system game $(H\ux = \uc)$ consists of 
\begin{enumerate}
	\item a pair of finite-dimensional Hilbert spaces $\calH_A$ and $\calH_B$; 
	\item a collection of binary observables $N_j$, $1 \leq j \leq n$, on $\calH_B$
	such that $N_j^2 = \1$ for every $1 \leq j \leq n$; 
	\item a collection of binary observables $M_{ij}$, $1\leq i \leq m$, $1\leq j\leq n$ 
	on $\calH_A$ such that 
	\begin{enumerate}
		\item $M_{ij}^2 = \1$ for every $i,j$,
		\item $\Pi_j M_{ij}^{H(i,j)} = (-\1)^{\uc(i)}$ for every $i$, and
		\item $M_{il}M_{ik} = M_{ik}M_{il}$ for every $i$ and $H(i,l) = H(i,k) =1$;
	\end{enumerate} 
	and
	\item a quantum state $\ket{\psi} \in \calH_A \x \calH_B$.
\end{enumerate}
\end{definition}
Note that any quantum strategy presented in terms of binary observables can be 
converted to a quantum strategy presented in terms of projective measurement by looking into
the spectral decompositions of the observables. 
\hf{More specifically, the fact that all the observables $\{M_{ij}\}_{j: H(i,j) = 1}$ commute with each other
implies that they share a common eigenspace. The collection of eigenvalues associated with one eigenstate is the assignment
to the whole equation when this eigenstate is measured in a projective measurement strategy.}
 \carl{If you're going to make that claim, you should make it more precise.  Add a sentence explaining briefly how the construction is done.}

@@

%=======================================
\section{The linear system game}
\label{sec:lsg}
%=======================================
In this section, we introduce a linear system game which is a component of the full test.
This game is designed to enforce relations that should be satisfied by 
Alice and Bob's observables. The inspiration comes from 
Slofstra's seminal work~\cite{slofstra2017}, in which he
embeds the group
\begin{align}
	K = \ip{ x,y,a,b:a^2=b^2=e, ab=ba, yay^{-1} = a, yby^{-1} = ab, xyx^{-1}=y^2}
\end{align}
into a linear system game such that the relations in the definition of $K$ can be derived from the
combination of the linear equations. Then he showed the difference between exact representations
and approximate representations of $K$, which implies that the set of quantum correlation is not closed.
\hf{We generalize the relation $xyx^{-1} = y^2$ and embed the 
following relation
$
uou^{-1} = o^r 
$
for some $r \in \N$ into a linear system game.}

%------------------------------------------------------------------------
\subsection{The embedding of $G$}
%------------------------------------------------------------------------
The main result of this subsection is summarized in the following theorem.
\begin{theorem}
	The relation $uou^{-1} = o^r$ can be embedded in a linear system game which has
	$n(r) := 18r+85$ variables and $m(r) := 17r + 77$ equations, where each equation has $3$ variables.
\end{theorem}
We prove this by constructing the solution group $\Gamma$ of the linear system game. 
We also prove some properties of the generators of $\Gamma$ along the way.

We embed $uou^{-1}= o^r$ into $\Gamma$ in three steps, which introduce two intermediate groups $G_0$ and $G_1$ defined below.
\begin{definition}	
\label{def:g0}
	The presentation of $G_0$ has order-$2$ generators:
	\begin{align*}
		\{o_i\}_{i=1}^{r} \cup \{u_i\}_{i=1}^5
	\end{align*}
	and relations:
	\begin{align*}
	&u_3 = u_2o_1u_2 && u_4 = u_2o_2u_2 \\
	&u_5 = u_1u_3u_1 && o_2 = u_1u_4u_1\\
	&u_5 = o_1 o_r o_1,
	\end{align*}
	and when $r$ is even
	\begin{align*}
	&o_{1+2j} = o_1o_{2j}o_1 && o_{2+2j} = o_2o_{1+2j}o_2&& \text{ for } j = 1 \dots r/2 - 1;
	\end{align*}
	when $r$ is odd
	\begin{align*}
	&o_3 = o_2o_1o_2 &&
	 o_{2+2j} =o_1o_{1+2j}o_1 && o_{3+2j} = o_2o_{2j+2}o_2 &&\text{ for } j = 1 \dots (r-3)/2.
	\end{align*}
\end{definition}
\begin{proposition}
	The group $G_0$ embeds the relation 
	\begin{align}
		(u_1u_2)^j o_1o_2 (u_2u_1)^j = (o_1o_2)^{r^j}, 
	\end{align}
	for any $ j \in \N$.
\end{proposition}
The proof follows the proof of Proposition~$4.8$ of Ref.~\cite{slofstra2017}
\begin{proof}
	We prove it by induction.
	Direct calculation gives us that
	\begin{align*} 
		u_1u_2 o_1o_2 u_2u_1 = &u_1 (u_2 o_1u_2) (u_2o_2 u_2) u_1 \\
	=& (u_1 u_3 u_1) (u_1 u_4 u_1)\\
	=& u_5 o_2\\
	=& o_1o_ro_1 o_2.
	\end{align*}
	Then we substitute the definitions of $o_k$ for $k = r \dots 3$ into the equation above and
	proves the $j=1$ case.

	Now assume the statement is true for $j = n$, then for $j = n+1$
	\begin{align*}
		(u_1u_2)^{n+1} o_1o_2 (u_2u_1)^{n+1} =& u_1u_2 (o_1o_2)^{r^n} u_2u_1 \\ 
		 =& (u_1u_2 o_1o_2 u_2u_1)^{r^n} \\
		 =& (o_1o_2)^{r^{n+1}},
	\end{align*}
	where from the first line to the second line, we insert $(u_2u_1)(u_1u_2)$ between every pair of $o_1o_2$.
	Hence, the statement is true.
\end{proof}
To better characterize all the conjugation relations above and simplify the form of $G_1$ defined below, 
we relabel $u_i$ and $o_i$'s
as $a_i$'s such that
\begin{align}
	a_j := 
	\begin{cases}
	 o_j \text{ for } j = 1,2 \\
	 u_{j-2} \text{ for } j = 3\dots 7 \\
	o_{j- 5} \text{ for } j = 8 \dots r+5.
	\end{cases}
\end{align}
Then we define the set $C(r)$ of tuples $(i,j,k)$ such that
\begin{align*}
	(i,j,k) \in C(r) \iff a_ia_ja_i = a_k.
\end{align*}
The size of $C(r)$ is $r+3$. 
%We can also employ some ordering of $C(r)$ such that $C(r,j)$ is a unique tuple for 
%$j = 1 \dots r+3$.
In this way, the group $G_0$ can be presented by
$
G_0  = \ip{ \{a_i\}_{i=1}^{r+5} : C(r) }.
$
Then we define the group $G_1$.
\begin{definition}
The presentation of $G_1$ has order-$2$ generators:
\begin{align*}
	\{a_i, b_i, c_i, d_i, v_i\}_{i=1}^{r+5}, f, g, \{h_{jk}\}_{(i,j,k) \in C(r)};
\end{align*}
and relations:
\begin{align*}
	&a_i = b_ic_i = fd_i = gv_i,&& fb_if =c_i &&\text{ for } i= 1 \dots r+5 \\
	&h_{jk}b_j c_k = e,&& d_ib_jd_i = c_k &&\text{ for all } (i,j,k) \in C(r).
\end{align*}
\end{definition}
Note that the group $G_1$ is slightly different from the group $K$ used in the proof of Lemma~$4.4$ of Ref.~\cite{slofstra2017}.
We introduce the generator $g$ so that later we can associate $f$ with $g$ in linear relations of the Magic Square game.
Such relations are important for the self-testing proof.
Two important properties of $G_1$ are given in propositions below.
The first property of $G_1$ was first proved in Lemma~$4.4$ of \cite{slofstra2017}.
\begin{proposition}
	The group $G_1$ embeds relation $x_ix_jx_i = x_k$ for all $(i,j,k) \in C(r)$.
\end{proposition}
\begin{proof}
	We first show that $d_i c_j d_i = b_k$, which is because
	\begin{align*}
		d_i c_j d_i = d_i (f b_j f) d_i = f (d_i b_j d_i) f = f c_k f = b_k.
	\end{align*}
	Then, we can prove that 
	\begin{align*}
		a_i a_j a_i = f d_i b_j c_j f d_i = (f d_i b_j d_i f)(f d_i c_j d_i f) = (f c_k f)(f b_k f) = b_k c_k = a_k. 
	\end{align*}
\end{proof}
\begin{proposition}
	In the group $G_1$, the generators $f$ and $g$ commute with $a_i$ for all $i = 1 \dots r+5$.
\end{proposition}
\begin{proof}
	We can check that
	\begin{align*}
		fa_i f a_i = d_i d_i = e && g a_i g a_i = v_i v_i  = e,
	\end{align*}
	for all $i = 1 \dots r+5$.
\end{proof}
Note that there are two types of conjugacy relations in $G_1$. One is of the form
$f b_i f = c_i$ for all $i = 1 \dots r+5$. The other one is of the form 
$d_ib_jd_i = c_k$ for all $(i,j,k) \in C(r)$. For each type of the conjugacy relations, 
we are going to embed it into a different set of linear relations in $\Gamma$.

\begin{definition}
\label{def:gamma}
The presentation of $\Gamma$ has order-$2$ generators:
\begin{align*}
	J, \{a_i, b_i, c_i, d_i, v_i,w_i,\{ k_{i,j} \}_{j=1}^5\}_{i=1}^{r+5}, \{f_i,g_i,m_i\}_{i=0}^2, \{h_{jk}\}_{(i,j,k) \in C(r)}, 
	\{\{ k_{l,j} \}_{j=1}^6\}_{l \in C(r)},
\end{align*}
and relations:
\begin{itemize}
\item for all $i = 1 \dots r+5$:
\begin{align*}
	&a_i = b_ic_i = f_0d_i = g_0v_i \\
	&g_2 a_i w_i = e \\
	&f_0 f_1 f_2 = e && b_i f_2 k_{i,1} = e && k_{i,1} k_{i,2} k_{i,3} = e\\
	&f_0 k_{i,3} k_{i,4} = e && c_i k_{i,4} k_{i,5} =e && f_1 k_{i,2} k_{i,5} = e,
\end{align*}
which embed $f_0 b_i f_0 = c_i$;
\item for all $ l = (i,j,k) \in C(r)$:
\begin{align*}
	&h_{jk}b_j c_k = e\\
	&d_i k_{l,1} f_2 = e && b_j f_2 k_{l,2} = e && k_{l,2} k_{l,3} k_{l,4} = e\\
	&d_i k_{l,4} k_{l,5} = e && c_k k_{l,5} k_{l,6} =e && k_{l,1} k_{l,3} k_{l,6} = e,
\end{align*}
which embed $d_i b_j d_i = c_k$;
\item relations of a Magic Square game:
\begin{align*}
	&f_0 f_1 f_2 = e && g_0 g_1 g_2 = e &&m_0 m_1 m_2 = e \\
	&f_0 g_2 m_0 = e && f_2 g_0 m_1 = e && f_1 g_1 m_2 = J,
\end{align*}
which embed $f_0 g_0 f_0 g_0 = J$ and $f_2 g_2 f_2 g_2 = J$;
\item $J$ commutes with all the other generators.
\end{itemize}
\end{definition}
The special properties of the generators of $\Gamma$ are summarized in the two propositions below.
\begin{proposition}
	The group $\Gamma$ embeds all the conjugacy relations of $G_1$.
	It also embeds the relations: $f_0 g_0 f_0 g_0 = J$ and $f_2 g_2 f_2 g_2 = J$.
\end{proposition}
The proof of the proposition above follows the proof of Proposition $4.2$ of Ref.~\cite{slofstra2017}.
\begin{proposition}
	In the group $\Gamma$, the generator $f_2$ commutes with $f_0$ and $a_i$ for all $i = 1 \dots r+5$;
	the generator $g_2$ commutes with $g_0$ and $a_i$ for all $i = 1 \dots r+5$.
\end{proposition}
\begin{proof}
	We show the commutativity property of $f_2$ as an example. The proof for $g_2$ is very similar.
	The commutativity between $f_0$ and $f_2$ is immediate from the relations.
	From the relation, we can also deduce that $f_2$ commutes with $b_i$ for all $i$.
	Since $a_i =b_ic_i = b_i f_0 b_i f_0$, we know $f_2$ commutes with $a_i$.
\end{proof}

%------------------------------------------------------------------------
\subsection{The representation of $\Gamma$}
%------------------------------------------------------------------------
In this section we give a representation of $\Gamma$ which is built upon the representation 
$\Psi_0$ of $G_0$ and $\Psi_1$ of $G_1$. We need the representation of $\Gamma$ to construct the
ideal strategy that realizes our correlation.

Before giving the representations, we define two Hilbert spaces $W_{d-1}$ and $W_2$, which will form the carrier spaces
of the representations,
\begin{align}
	\label{eq:w_subspace}
	W_{d-1} := \spn(\{\ket{x_j}\}_{j=1}^{d-1}) && W_2 = \spn(\ket{x_1}, \ket{x_2}).
\end{align}
Note that another form of the basis of $W_{d-1}$ is $\{\ket{x_{r^j}}\}_{j=0}^{d-2}$, where the subscript $r^j$ is taken
modulo $d$ implicitly. We use the second form of the basis when it is convenient.
We denote the identity operator for these two spaces by $\1_{W_{d-1}}$ and $\1_{W_2}$.
On the Hilbert space $W_2$, we define
\begin{align}
	X_{W_2} = \ketbra{x_1}{x_2} + \ketbra{x_2}{x_1} &&
	Y_{W_2} = i\ketbra{x_1}{x_2} - i \ketbra{x_2}{x_1} &&
	Z_{W_2} = \ketbra{x_1}{x_1} - \ketbra{x_2}{x_2},
\end{align}
\begin{definition}
The representation, $\Psi_0$, of $G_0$ on $W_{d-1}$ is defined by
\begin{align}
	\Psi_0(a_1) =&\sum_{j=1}^{(d-1)/2} \omega_d^j \ketbra{x_j}{x_{d-j}} + \omega_d^{-j} \ketbra{x_{d-j}}{x_{j}} \\
	\Psi_0(a_2) = &\sum_{j=1}^{d-1} \ketbra{x_j}{x_{d-j}}\\
	\Psi_0(a_3) = &\ketbra{u_0}{u_0} +\omega_{d-1}^{(d-1)/2}\ketbra{u_{(d-1)/2}}{u_{(d-1)/2}}\\ + 
	&\sum_{k=1}^{(d-3)/2}\left( \omega_{d-1}^k\ketbra{u_k}{u_{d-1-k}} + \omega_{d-1}^{-k}\ketbra{x_{d-1-k}}{x_k}\right)\\ 
	\Psi_0(a_4) = &\ketbra{u_0}{u_0} +\ketbra{u_{(d-1)/2}}{u_{(d-1)/2}} \\+
	 &\sum_{k=1}^{(d-3)/2}\left(\ketbra{u_{d-1-k}}{u_k} + \ketbra{u_k}{u_{d-1-k}}\right),
\end{align}
where $\{ \ket{u_j} \}_{j=0}^{d-2}$ is a another basis of $W_{d-1}$ given by
\begin{align}
	\ket{u_k} = \frac{1}{\sqrt{d-1}} \sum_{j=0}^{d-2} \omega_{d-1}^{jk} \ket{x_{r^j}}.
\end{align}
The representation of the rest of the generators
can be constructed from $\Psi_0(a_1)$, $\Psi_0(a_2)$, $\Psi_0(a_3)$ and $\Psi_0(a_4)$ following the 
conjugation relations.
\end{definition}
We can check that
\begin{align}
	\Psi_0(a_1a_2) =  \sum_{j=0}^{d-2} \omega_d^{r^j} \ketbra{x_{r^j}}{x_{r^j}} &&
	\Psi_0(a_3a_4) =  \sum_{j=0}^{d-2} \ketbra{x_{r^{j-1}}}{x_{r^j}},
\end{align}
which satisfy the relation $\Psi_0(a_3a_4) \Psi_0(a_1a_2) \Psi_0(a_4a_3) = \Psi_0(a_1a_2)^r$ and
$[\Psi_0(a_3a_4), \Psi_0(a_2)] = \1_{W_{d-1}}$.
